\begin{frame}[parent={cmap:jabuti-gui},hasnext=true,hasprev=true]
\frametitle{Main functionalities}
\framesubtitle{Properties}
\label{concept:properties-menu}

\begin{block}{Properties}
The \highlight{Properties} menu provides general configuration options.
\end{block}

\begin{block}{Available properties}<2->
\begin{itemize}
	\item<+-> \highlight{Look and Feel}: allows to change the look and feel
	style considering different options: Metal (default), Motif, and
	Windows.

	\item<+-> \highlight{Project Manager}: allows to verify and change the
	current set of classes under testing in the current project.

	\item<+-> \highlight{Test Server}: handles the configuration of the test
	server.

	\item<+-> \highlight{Available Memory Dialog}: shows current available
	memory on system.
\end{itemize}
\end{block}
\end{frame}


\begin{frame}
\frametitle{Main functionalities}
\framesubtitle{Properties}
\label{concept:look-and-feel}

\begin{block}{Look and Feel}
\highlight{Look and Feel} allows to change the look and feel style considering
different options: Metal (default), Motif, and Windows.
\end{block}

\begin{block}{Demo}
\insertmovie{resources/JaBUTi/JaBUTi-GUI/JaBUTi-GUI-Properties-LookAndFeel/JaBUTi-GUI-Properties-LookAndFeel}
\end{block}
\end{frame}


\begin{frame}
\frametitle{Main functionalities}
\framesubtitle{Properties}
\label{concept:project-manager}

\begin{block}{Project Manager}
\highlight{Project Manager} allows to verify and change the current set of
classes under testing in the current project.
\end{block}

\begin{block}{Demo}
\insertmovie{resources/JaBUTi/JaBUTi-GUI/JaBUTi-GUI-Properties-ProjectManager/JaBUTi-GUI-Properties-ProjectManager}
\end{block}
\end{frame}


\begin{frame}
\frametitle{Main functionalities}
\framesubtitle{Properties}
\label{concept:test-server}

\begin{block}{Test Server}
\highlight{Test Server} handles the configuration of the test server.
\end{block}

\begin{block}{Demo}
\insertmovie{resources/JaBUTi/JaBUTi-GUI/JaBUTi-GUI-Properties-TestServer/JaBUTi-GUI-Properties-TestServer}
\end{block}
\end{frame}


\begin{frame}
\frametitle{Main functionalities}
\framesubtitle{Properties}
\label{concept:available-memory-dialog}

\begin{block}{Available Memory Dialog}
\highlight{Available Memory Dialog} shows current available memory on system.
\end{block}

\begin{block}{Demo}
\insertmovie{resources/JaBUTi/JaBUTi-GUI/JaBUTi-GUI-Properties-AvailableMemoryDialog/JaBUTi-GUI-Properties-AvailableMemoryDialog}
\end{block}
\end{frame}
