\begin{frame}[hasprev=false, hasnext=true]
\label{example:triangle}
\frametitle{Triangle}
\framesubtitle{Description}

\begin{block}{Software requirements specification}
The software read three  values that represents the edges of a triangle.
For those values, the software should write if the triangle is isosceles,
scalene, or equilateral.
\end{block}

\begin{block}{Your task}
\begin{itemize}
	\item You were hired to develop this software. How would you do it? Think
	about:
	\begin{itemize}
		\item design,
		\item implementation,
		\item testing.
	\end{itemize}
\end{itemize}
\end{block}
\end{frame}



\begin{frame}[hasprev=true, hasnext=true]
\frametitle{Triangle}
\framesubtitle{Problem}

\begin{block}{My task}
\begin{itemize}
	\item I was the guy that hired you to implement software.

	\item As soon as you deliver the first release of the software, I came up
	with several issues.
\end{itemize}
\end{block}

\begin{block:fact}{Issues}
\begin{itemize}
	\item Why the triangle (5, 5, 3) was not recognized as isosceles?

	\item Why did the software accepted triangles which the sum of two edges
	is less than the third edge?

	\item Why did the software accepted triangles which edges are zero?

	\item Why did the software accepted triangles which edges are negative?

	\item Why did the software accepted triangles which edges are not even a
	number?
\end{itemize}
\end{block:fact}
\end{frame}


\begin{frame}
\frametitle{Triangle}
\framesubtitle{Diagnostic}

\begin{block:fact}{Diagnostic}
\begin{itemize}
	\item The software requirement specification was far from complete (many
	implicit requirements).

	\item Nonetheless, several errors could be caught it test cases were
	designed for the software \textbf{before} delivering or even implementing
	it.
\end{itemize}
\end{block:fact}
\end{frame}



\begin{frame}[hasprev=true,hasnext=false]
\frametitle{Triangle}
\framesubtitle{Diagnostic}

\begin{block:fact}{Did you tested for\dots}
\begin{itemize}
	\item a valid scalene triangle?
	\item a valid isosceles triangle?
	\item a valid equilateral triangle?
	\item valid isosceles triangles (with permutated edges)?
	\item a value of zero?
	\item negative values?
	\item the sum of two edges is equal to the third edge?
	\item the sum of two edges is less than the third edge?
	\item all edges with a value of zero?
    \item non-integer values?
    \item insufficient values (e.g., 2 instead of 3 edges)?
    \item the correct triangle type for the specified input in all the previous
    tests?
\end{itemize}
\end{block:fact}
\end{frame}