\begin{frame}[parent={cmap:structural-software-testing},hasnext=true,hasprev=true]
\frametitle{Complexity-based test criterion}
\label{concept:complexity-based-test-criterion}

\begin{block:concept}{Definition}
Complexity-based test criterion uses information about program complexity
in order to derive test requirements.
\end{block:concept}

\begin{block:fact}{Complexity-based test criteria}
\begin{itemize}
	\item A well known complexity-based test criterion is the McCabe's
	criterion.
\end{itemize}
\end{block:fact}
\end{frame}


\begin{frame}
\label{concept:mccabe-criterion}
\frametitle{Complexity-based criterion}
\framesubtitle{McCabe's criterion}

\begin{block:concept}{Definition}
The McCabe's criterion requires a set of linearly independent complete paths
from the control flow graph to be traversed by the execution of the test set.
\end{block:concept}

\begin{block:fact}{}
\begin{itemize}
	\item The McCabe's criterion uses the cyclomatic complexity to derive the
	set of testing requirements.

	\item Satisfying McCabe's criterion automatically guarantees both
	decision coverage (All-edges) and statement coverage (All-nodes).
\end{itemize}
\end{block:fact}
\end{frame}



\begin{frame}
\label{procedure:mccabe-criterion}
\frametitle{Complexity-based criterion}
\framesubtitle{McCabe's criterion}

\begin{block:procedure}{}
\begin{enumerate}
	\item Derive the CFG from the software module.
	\item Compute the graph's Cyclomatic Complexity (C).
	\item Select a set of C linearly independent paths.
	\begin{enumerate}
		\item Pick a baseline path (it must be a complete path).
		\begin{enumerate}
			\item This path should be a reasonably typical path of execution
			rather than an exception processing path.

			\item The best choice would be the most important path from the
			tester's viewpoint.
		\end{enumerate}

		\item To choose the next path, change the outcome of the first decision
		along the baseline path while keeping the maximum number of other
		decisions the same as the baseline path.

		\item Generate the remaining paths by varying the remaining decisions,
		one by one.
	\end{enumerate}
	\item Create a test case for each basis path.
\end{enumerate}
\end{block:procedure}


\hfill
\hyperlink{example:mccabe}{\beamerbutton{Example: McCabe's criterion example}}
\end{frame}
